Concurrent Programming with CXL

### 2020-06-16 book/paper.tex
Latest

@@

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/DinersCV.cxl}
\end{code}
\caption{[DinersCV.cxl] Dining Philosophers that grab both forks at the same time.}
\label{fig:dinerscv}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/DinersAvoid.cxl}
\end{code}
\caption{[DinersAvoid.cxl] Dining Philosophers that carefully avoid getting into a deadlock
scenario.}
\label{fig:dinersavoid}
\end{figure}

@@

To implement a \emph{No Hold and Wait} solution, a philosopher would need a
way to lock both the left and right forks at the same time.  Locks do not
have such an ability, and neither do semaphores, so we re-implement the
Dining Philosophers using condition variables that allow one to wait for
arbitrary application-specific conditions.
